
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\subsection{Adaptive wavenumber filtering}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Adaptive wavenumber filtering is a well-established method for processing of images of propagating elastic waves.
The method has proved to be useful for crack size estimation~\cite{Kudela2015}, impact induced damage assessment~\cite{Kudela2018},  delamination and disbonding detection and localisation~\cite{Radzienski2019a}.  
It is used here as a reference point for comparison purposes against proposed strategies based on FCN.

The method involves steps such as 2D Fourier Transform, wavenumber filtering, inverse Fourier Transform and RMS.
It can be used as an automated tool for producing damage maps which are easy in interpretation.
However, it still requires setting a threshold for the filter mask and quantisation threshold useful for damage size estimation.
These thresholds can be estimated empirically and even certain rigid range of thresholds will lead to satisfactory results.
Nevertheless, it is not a fully automatic process.
FCN based approach seems to have an advantage in this regard.
On the other hand, FCN would also need some prior inductive bias from the domain knowledge such as pre-processing parameters, supervision into assigned class, and the most important one: assumption that pixels of processed images can be categorized as damaged and undamaged.
Moreover, the training of FCN requires tuning of many hyperparameters such as  learning rate, momentum, choice of optimizer, dropout rate, batch size, etc. 
But this process must be completed only once.