%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Composite materials are very prone to various kinds of defects such as cracks, fiber breakage, debonding, and delamination~\cite{ip2004delamination, smith2009composite}. Among these defects, delamination is one of the most hazardous forms of the defects in composite materials which essentially leads to very catastrophic failures if not detected at early stages~\cite{valdes1999delamination}. Therefore, it is essential to effectively identify the delamination in composite structures for the purpose of safe and reliable implementation in various real-world applications. Different types of Structural Health Monitoring (SHM) techniques have been developed for delamination detection in composite structures. Recently, guided Lamb waves based SHM gained high popularity for damage detection in composite structures~\cite{mitra2016guided}. This increasing use of Lamb waves in SHM is due to their higher sensitivity to minor defects, propagation with low attenuation, and potential to monitor large areas with low-voltage and only a small number of sparsely distributed transducers~\cite{alleyne1992interaction, giurgiutiu2003lamb, ihn2008pitch, mitra2016guided}. However, a smaller number of transducers are not very suitable for high-quality resolution damage maps. Whereas, the employment of a very dense array of transducers is also not feasible in most of the situations. For alleviating such problem Scanning Laser Doppler Vibrometer (SLDV) is employed. SLDV is capable to measure guided Lamb waves in a very dense grid of points over the surface of a large specimen. This collection of signals is known as full wavefield~\cite{radzienski2019damage}. Full wavefield processing techniques are capable of effectively estimating the size and location of damage which is very cumbersome to acquire with the use of transducer arrays~\cite{girolamo2018impact, kudela2018impact}. From the last few years, full wavefield signals are continually being assessed for the detection and localisation of defects in composite structures~\cite{sohn2011delamination, sohn2011automated, rogge2013characterization, kudela2018impact, radzienski2019damage}.

Currently, full wavefield image based damage detection techniques are employing various physics and classical machine learning-based methods. These structural damage detection approaches are composed of two processes: feature extraction and feature classification. The feature extraction process usually needs a great deal of human labor and computational effort which prevents the applicability of these techniques in real-time SHM utilization. These systems also needs a notable amount of expertise from the practitioner, which is almost impossible to be always available. Moreover, in many situations, the extracted handcrafted features by these techniques also fail to precisely characterise the acquired signal which leads to poor classification performance~\cite{zhao2019deep, yuan2020machine}. These systems are also not suitable for modeling large-scale data.

Recently, deep learning, a branch of machine learning which is originated from Artificial Neural Network (ANN) has shown very promising results in various domains such as computer vision, object detection, speech recognition, remote sensing, medical sciences and many more~\cite{deng2014deep, mohanty2016using, zhang2020well, pashaei2020review}. Various deep learning architectures have been developed up to date~\cite{zhao2019deep}. In recent years, deep learning has shown significant improvements in image segmentation due to the advancement in deep Convolutional Neural Networks (CNN). Image segmentation is a fundamental component in numerous visual recognition systems. Image segmentation has widely been employed in autonomous driving~\cite{zhang2013understanding, cordts2016cityscapes, ros2016synthia, li2018real}, medical applications~\cite{taghanaki2020deep}, agriculture sciences~\cite{milioto2018real}, augmented reality~\cite{miksik2015semantic} and many more. Image segmentation techniques partition images or video frames into multiple objects or segments~\cite{szeliski2010computer}. Image segmentation can be expressed as a pixel-level classification problem with semantic labels, which is known as semantic segmentation or it can be partitioning the images into individual objects which are called instance segmentation. Semantic segmentation functions on pixel-wise labeling with a set of object categories of an image. Therefore, it is generally a more difficult task than image classification, which only predicts a single label for the entire image~\cite{minaee2020image}. Semantic segmentation of images is one of the most challenging problems in computer vision. It is also a primary prerequisite for different hot topics in computer vision. Semantic image segmentation not only depends on the semantics in the question but also on the problem that needs to be addressed~\cite{ghosh2019understanding}.

Deep learning-based systems intend to derive hierarchical representations from the input data via constructing deep neural networks by multiple layers of non-linear transformations. In deep learning architectures, the output of one layer act as the input to the other subsequent layer. The application of one layer in deep learning acquires a new representation of the input data and then, the stacking composition of many layers enables the model to learn complex concepts from the simple notions that can be formed from raw input. Additionally, the deep learning-based system can learn internal representations automatically from the raw input data and then predict targets. Therefore, these systems do not need extensive human labor and information for hand-crafted feature design~\cite{zhao2019deep, yuan2020machine}.

Deep learning techniques have widely been utilized for the inspection and maintenance of civil infrastructure and has shown very promising results ~\cite{cha2017deep, lin2017structural, liu2019computer}. It has also been successfully applied for various fault diagnosis based tasks in rotating machinery~\cite{jia2016deep, janssens2016convolutional}. However, deep learning is still less explored for the purpose of delamination detection in composite materials.   

Few researchers have applied various deep learning techniques for damage detection with guided Lamb waves in composite structures. Mardanshahi et al.~\cite{mardanshahi2020detection} applied different classification and detection techniques for matrix cracking in the polymeric composite structures. They acquired the data with Lamb wave propagation using different matrix crack densities. Three machine learning algorithms naming Support Vector Machine (SVM), multilayer perceptron (MLP), and Linear vector quantization (LVQ) neural network (NN) were applied on the dimensionality reduced data by Linear Discriminant Analysis (LDA). They showed that the SVM based classifier achieved highest accuracy on their data having an accuracy of 91.7\%, while LVQ NN and MLP NN shown 88.9\% and 77.8\% accuracies respectively. Fenza et al.~\cite{de2015application} presented the utilization of ANN and probability ellipse techniques for the detection, location, and degree of defects in aluminum and fabric composite plates with the use of Lamb waves. Both the ANN and probability ellipse techniques were based on the damage index assessed by examining the variations in the Lamb waves acquired before and after the damage in each analyzed path. The results from both methods proved that guided Lamb waves have prominent advantages in localisation and the detection of different kinds of defects in plate-like structures. Feng et al.~\cite{feng2019locating} proposed two time of flight (ToF) based algorithms of scattered guided Lamb waves in carbon fiber reinforced polymer (CFRP) plates. Their first algorithm is a probabilistic approach that constructs a probability matrix. The probability matrix is used for the localisation of defects while the second algorithm is based on ANN which is then employed for improving the accuracy of defect localisation. The neural network receives the input from the ToF of scattered waves acquired from three sensor pairs. Chetwynd et al.~\cite{chetwynd2008damage} used MLP neural network for the classification and regression tasks of damage detection in a stiffened curved CFRP investigated using Lamb waves with the use of eight surface bonded piezoelectric transducers. Many localised defects were fabricated through a force applicator, and Lamb wave responses were received for the damaged and healthy cases. For each case, the Lamb wave response was then transformed into a scalar novelty index with the help of outlier analysis. These novelty indices of 28 sensor paths were then provided as input to the MLP classification and regression architectures. For the classification of damaged and undamaged regions of the panel, the MLP classificier was employed, whereas the MLP regressor was used for evaluating the accurate location of damage on the panel. They achieved quite better results with both the classifier and regerssor. The classification accuracy of their MLP based classifier was 88.1\% on the test data while the Mean Square Error (MSE) value of the regerssor was 3.1\% on the unseen data. Su and Ye~\cite{su2004lamb} presented a Lamb wave based delamination identification technique in composite structures with the use of wavelet transform and multi-layer feedforward ANN architecture. The ANN was employed with the error-backpropagation (BP) algorithm. They also developed an Intelligent Signal Processing and Pattern Recognition (ISPPR) package for the extraction and digitision of spectrographic characterisitics of simulated Lamb waves in the time-frequency domain, which is known as Digital Damage Fingerprints (DOF) and is used for constructing a Damage Parameters Database (DPD). The DPD is then employed offline for training the neural network. They validated their approach with identifying actual delamination in different composites and also proved that their system has achieved excellent quantitative diagnosis results for different damage parameters such as the presence, location, orientation and geometry of defects. Hussain et al.~\cite{hussaintemporal} proposed a Temporal Convolutional Network (TCN) based transfer learning system for delamination prediction in CFRP cross-ply laminates. They employed a CFRP dataset from NASA which is composed of signals from Lamb waves sensors and X-ray images of specimens for capturing the propagation of defects in carbon fiber composite under fatigue loading. The TCN model was trained with various combinations of lengths of the sensors signals and different frequencies at which Lamb wave signals were sensed. They demonstrated that their approach needs very little time for the training and can also predict the delamination on a new composite coupon by utilizing only a few samples of the test coupon. Melville et al.~\cite{melville2018structural} applied SVM and deep learning techniques for damage detection on full wavefield signals of ultrasonic guided wave images. The wavefield data was acquired via a laser Doppler vibrometer and piezoelectric actuators on thin metal plates. They showed that the deep learning methods achieved quite better damage prediction results as compared to the SVM based methods. Esfandabadi et al.~\cite{keshmiri2019deep} investigated the applications of super-resolution techniques to acquire high-resolution wavefields via the training of neural networks on different aluminum and CFRP plates. They applied two variants of CNN architecture: Super-Resolution Convolutional Neural Networks (SRCNNs) and Very-Deep Super Resolution (VDSR) with compressive sensing for the recovery of high spatial frequency information from low-resolution wavefield images. A dataset of 652 wavefield images (326 with defects and 326 without defects) were constructed, acquired with laser Doppler vibrometer of guided ultrasonic waves propagation. Additionally, 273 images of wavefield were employed as a testing database for the validation purpose of the proposed methodology.           

To the best of the authors' knowledge, no such study exists which emphasized deep learning-based segmentation techniques for damage detection on full wavefield analysis in composite structures.